R for Clinical Study Reports and Submission

### 2021-12-10 tlf-efficacy-km.Rmd
fix minor typo

# Create RTF figure
rtf_read_png("tlf/fig_km.png") %>% # Read PNG files from the file path
  rtf_title("Kaplan-Meier Plot for Time to First Dermatologic Event by Treatment Group", "All Participants") %>% # Add title or subtitle
  rtf_footnote("footnote") %>% # Add footnote
  rtf_source("[datasource: adam-adtte]") %>% # Add data source
  rtf_figure(fig_width = 6, fig_height = 3.6) %>% # Set proportional figure size to the original PNG figure size
  rtf_encode(doc_type = "figure") %>% # Encode rtf as figure
  write_rtf(file = "tlf/fig_km2.rtf")
```

@@

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("pdf/fig_km3.pdf")
```

>>>>

# Create RTF figure
rtf_read_png("tlf/fig_km2.png") %>% # Read PNG files from the file path
  rtf_title("Kaplan-Meier Plot for Time to First Dermatologic Event by Treatment Group", "All Participants") %>% # Add title or subtitle
  rtf_footnote("footnote") %>% # Add footnote
  rtf_source("[datasource: adam-adtte]") %>% # Add data source
  rtf_figure(fig_width = 6, fig_height = 3.6) %>% # Set proportional figure size to the original PNG figure size
  rtf_encode(doc_type = "figure") %>% # Encode rtf as figure
  write_rtf(file = "tlf/fig_km2.rtf")
```

@@

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/fig_km3.pdf")
```
